---
title: GHC Demo Assignment
subtitle: CSC 110 - Fall 2025
author: Addy Collins
date: last-modified
format:
  html:
    toc: true
    toc-location: body
    theme: flatly
  pdf:
    toc: true
---

# Setup

```{r}
#| include: false
library(tidyverse)
```

# Homework

```{r}
#| fig-cap: Fuel mileage scatterplot
#| fig-cap-location: top

ggplot(
  mpg,
  aes(
    x = displ,
    y = hwy
  )
) + 
  geom_point() +
  labs(
    title = "Impact of Vehicle Engine Size on Highway Fuel Mileage",
    x = "Vehicle Engine Size (displacement)",
    y = "Highway Fuel Mileage"
  )
```

### A link to davidson.edu

[Davidson College Website](davidson.edu)

### An unordered list of the other classes I'm taking this semester
Fall Semester Classes

* POL 336: Politics & the Media
* HUMES 103

### An ordered list of my top 3 favorite movies
 
Top 3 Favorite Movies

1. Dead Poets Society
2. SCREAM (original)
3. Boyz in the Hood

### A footnote

Here is a footnote[^1]

[^1]: footnote reference stuff

### An equation showing the quadratic formula in display mode

display math:

$$x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$$

### A flowchart diagram in Mermaid

```{mermaid}
flowchart LR
  A(Professor Benbow gives an assignment) --> B[I recieve the assignment]
  B --> C{I decide when I wil do the assignment}
  C --> D[I complete it as planned]
  D --> E[I turn it in]
  C --> F[I procrastinate]
  F --> G[I work late]
  G --> E[I turn it in]
```

### A blockquote

> "Four score and seven years ago our fathers brought forth upon this continent a new nation, conceived in liberty, and dedicated to the proposition that all men are created equal."

### Three callout blocks

:::{.callout-note}
Just wanted you to make note of this first callout block
:::

:::{.callout-tip}
Here's a tip, check out my second callout block!
:::

:::{.callout-important collapse="true"}
It's important that you see how awesome it is that this callout black can collapse!
:::

{{< pagebreak >}}

# Reflection

### Links

**Links** will be useful in my final project because I will be able to provide a direct route to the places I gathered information (I can even put the link to a source in a footnote!) or point my audience to where they can learn more on a topic that I may not be able to go super in depth about. This is a powerful tool for context/empowering the people viewing my page to be curious and informed. Links also make it easy to give credit in a meaningful way. That isn't to say that I won't cite sources in MLA format or other, but rather that those citation methods sometimes don't make it easy for an audience member to quickly check out a source. *Links mean that I can make sure the audience has both proper citations and easily accessible ones.*

### Flowchart diagram in Mermaid

**Flowchart diagrams in Mermaid** will make showing/explaining methodology or process in my final project easier. I will be able to visually display my exploratory data analysis process, which makes it much easier to understand. *Actions/steps might take paragraphs to explain can be streamlined into digestible visuals that keep my audience engaged while they gain key understanding of my methods.*

### Callout blocks

**Callout blocks** will also be useful in my final project.I will be able to insert short explanations that may not be central to a point, but helpful in understanding. I can quickly point out or make note of certain choices without having to wander off on a tangent during an explanation of something else. I can provide tips for understanding a graph, or definitions of words that an average person might not know. I can also highlight key points and call attention to central ideas. Additionally, I can make my callout blocks collapsable so that when the audience isn't using them, they can be out of the way!